\papertitle

### 2012-10-13 manuscript.tex
Added Floreano textbook reference.
Minor additions

%............................................................................%
\subsubsection{Emission Model}

@@

To model the yaw motion of the ornithopter, we developed a one-dimensional model using the physical heading angle as the output and the heading angle set by the ground station as the input. This model accounts for both the yaw dynamics of the ornithopter and the internal PID controller on the actuator inputs for the tail rotor. We decided upon a one-dimensional model to reduce the complexity of the overall model and enable simple angle inputs and outputs, which is similar to our methods during experiementation. The format of the model we decided up on is shown in Equation~\ref{eq:plain_model}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.

>>>>

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs \naive

@@

To model the yaw motion of the ornithopter, we developed a one-dimensional model using the physical heading angle as the output and the heading angle set by the ground station as the input. This model accounts for both the yaw dynamics of the ornithopter and the internal PID controller on the actuator inputs for the tail rotor. We decided upon a one-dimensional model to reduce the complexity of the overall model and enable simple angle inputs and outputs, which is similar to our methods during experimentation. The format of the model we decided up on is shown in Equation~\ref{eq:plain_model}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.
